Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/results.tex
add info on times of main results

%!TEX root = ClementiBarba2020.tex

>>>>

%!TEX root = ClementiBarba2020.tex
All the results of these paper were obtained using \pygbe (\url{https://github.com/pygbe/pygbe})
with the version at this point in the history of commits (\url{https://github.com/pygbe/pygbe/tree/e1f3650b0c99cab99dcfe5372200d3a1534eddfe}), which contains 
the Dockerfile to create the image that was used for the containers where the simulations where run.

All results were obtained on a lab workstation, built from parts.
Hardware specifications are as follows: 
\begin{itemize}
  \item CPU: Intel Core i7-5930K Haswell-E 6-Core 3.5GHz LGA 2011-v3
  \item RAM: G.SKILL Ripjaws 4 series 32GB (4 x 8GB)
  \item GPU: Nvidia Tesla K40c (with 12 GB memory)
\end{itemize}

\textbf{Solver parameters}: We used a GMRES tolerance of $1\times10^{-6}$ for all our simulations. Details on the treecode and integration parameters, 
can be found with input files the archive repository.

\textbf{Run times:} We reported detailed time files along with the data of our simulations, that can be found in the repro-packs. However, 
here is a small report.

For the result of the replication of Figure 4 of Rockstuhl et al.\ the total time for each curve was approximately 11.6 hours, which is the result of computing
the extinction cross section for 175 wavelength cases, what gives us $\approx$4 minutes per run. In the case of the validation and replication of Figure 2a of Ellis et al. \  
the total time for the curve was approximately 2.3 hours, which is the result of computing
the extinction cross section for 208 wavelength cases, what gives us $\approx$40 seconds per run.
